---
title: "DAVIS-ALLISON-ADA-HOMEWORK-04"
author: "Allison Davis and Caitlin Leslie"
date: "April 12, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### ** This homework is a collaboration of myself, Allison Davis, and Caitlin Leslie. **

## Bootstrapping to estimate standard errors and CIs for linear models

  * Part 1: create linear model of log-home range by log-female body mass and report coefficients (slope and intercept).
```{r}
library(curl)
f <- curl("https://raw.githubusercontent.com/difiore/ADA-2019/master/KamilarAndCooperData.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = TRUE)
head(d)

d$home <- log(d$HomeRange_km2)
d$mass <- log(d$Body_mass_female_mean)
d <- d[complete.cases(d[ ,c("home", "mass")]), ]
head(d)


mod <- lm(data = d, home~mass)
(betas <- coef(mod))
```
    - Slope: 1.036
    - Intercept: -9.441
    
  * Part 2: Use bootstrapping to sample data 1000 times, fitting the same model and calculating the appropriate coefficients, to create sampling distribution around each beta. Plot histogram.

```{r}
sim <- NULL  
n <- length(d$home)
for (i in 1:1000) {
    sim[i] <- lm(data=(sample(d, n, replace = TRUE)), home~mass)
}
hist(sim, xlab = "Log-mass of Females", main = "Distribution of Home Ranges", breaks = 20)
abline(v = mean(sim), col = "blue")  
abline(v = mean(x), col = "red")  
ci <- normalCI(x, 0.95) 
abline(v = ci[1], col = "red") 
abline(v = ci[2], col = "red") 

```